State Results

### 2023-07-17 reports/state_figures.Rmd
include variant data from across the entirety of 2021

state_res %>%
  filter(state == "MI" & version %in% c("v7")) %>%
 # filter(state %in% sample(corrected$state,5)) %>%
  filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill =vlabel),
           #  fill = "#3E3D3D",
             alpha = .5,
             show.legend=FALSE) +
  # geom_ribbon(aes(x = date,
  #                 fill = 'Covidestim',
  #                 ymin = infections.lo,
  #                 ymax = infections.hi),
  #             alpha = .5) +
  # facet_grid(~vlabel, scales = "free_y",
  #             labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(legend.position="top") +
  # theme_c(axis.text.x = element_text(size = 16),
  #         axis.title.y = element_text(size=13),
  #         plot.title=element_text(face = "bold",
  #                                 hjust = .5, 
  #                                 size = 24,
  #                                 margin=margin(5,5,15,5,'pt')),
  #         strip.background = element_rect(fill = "#393939"),
  #         strip.text = element_text(color =  "white", size = 16),
  #         strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
  #                                     size = 22,
  #                                     face="bold"),
  #         strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
  #                                      face = "bold",
  #                                      size = 22),
  #         plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
  #                                      face = "italic"),
  #         legend.position = "top",
  #         legend.text =element_text(size = 17),
  #         legend.title = element_text(size=18, face="bold")) +
  geom_line(aes(x=week, y=share*m,
                color =variant_category,
                group=variant_category),
            data=variant,
            linewidth=1.3) +
  # scale_fill_manual(values =pal,
  #                   labels = TeX(names(pal)),
  #                    breaks='Covidestim',
  #                   name='')  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./m, name="Variant Proportion"),
                     labels = comma) +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Michigan"),
       color = "SARS-CoV-2 Variant",
       x="Date") +
  guides(color = guide_legend(override.aes = list(linewidth =3),
                              ncol=2,title.position="top")) +
 # scale_color_brewer(palette="Accent") 
  scale_color_manual(values=varpal) +
  scale_fill_manual(values=pal)

>>>>

state_res %>%
  filter(state == "MI" & version %in% c("v7")) %>%
 # filter(state %in% sample(corrected$state,5)) %>%
 # filter(biweek >=6) %>%
  group_by(biweek) %>%
  mutate(xmin = min(date),
         xmax = max(date)) %>%
  ungroup() %>%
   ggplot() +
  geom_ribbon(aes(x = date, 
             ymin = exp_cases_lb,
             ymax = exp_cases_ub,
             fill =vlabel),
           #  fill = "#3E3D3D",
             alpha = .5,
             show.legend=FALSE) +
  # geom_ribbon(aes(x = date,
  #                 fill = 'Covidestim',
  #                 ymin = infections.lo,
  #                 ymax = infections.hi),
  #             alpha = .5) +
  # facet_grid(~vlabel, scales = "free_y",
  #             labeller= labeller(vlabel =as_labeller(TeX, default=label_parsed))) +
  scale_x_date(date_breaks = "2 months", 
               date_labels = "%b %Y") +
  theme_c(legend.position="top") +
  # theme_c(axis.text.x = element_text(size = 16),
  #         axis.title.y = element_text(size=13),
  #         plot.title=element_text(face = "bold",
  #                                 hjust = .5, 
  #                                 size = 24,
  #                                 margin=margin(5,5,15,5,'pt')),
  #         strip.background = element_rect(fill = "#393939"),
  #         strip.text = element_text(color =  "white", size = 16),
  #         strip.text.y = element_text(margin = margin(5,5,5,5,'pt'),
  #                                     size = 22,
  #                                     face="bold"),
  #         strip.text.x =  element_text(margin = margin(5,3,5,3,'pt'),
  #                                      face = "bold",
  #                                      size = 22),
  #         plot.subtitle = ggtext::element_markdown(size = 25,margin = margin(3,5,10,5,'pt'),
  #                                      face = "italic"),
  #         legend.position = "top",
  #         legend.text =element_text(size = 17),
  #         legend.title = element_text(size=18, face="bold")) +
  geom_line(aes(x=week, y=share*m,
                color =variant_category,
                group=variant_category),
            data=variant,
            linewidth=1.3) +
  # scale_fill_manual(values =pal,
  #                   labels = TeX(names(pal)),
  #                    breaks='Covidestim',
  #                   name='')  +
  scale_y_continuous(sec.axis = sec_axis( trans=~./m, name="Variant Proportion"),
                     labels = comma) +
  labs(y = "Estimated Infections",
       title = paste0("Estimated Infections by Version in Michigan"),
       color = "SARS-CoV-2 Variant",
       x="Date") +
  guides(color = guide_legend(override.aes = list(linewidth =3),
                              ncol=2,title.position="top")) +
 # scale_color_brewer(palette="Accent") 
  scale_color_manual(values=varpal) +
  scale_fill_manual(values=pal)
